TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems

### 2017-02-11 ISORC2017/paper.tex
Add the option for figures
Add the figures and tables of evaluations

@@

This paper proposes component-based TCP/IP protocol stack, i.e., TINET+TECS, to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.

In addition, the proposed framework utilizes dynamic connection, a novel method of TECS, to switch component bindings dynamically.
A general TCP/IP protocol server dynamically processes the requested port i.e., HTTP (port: 80), HTTPS (prot: 443).
However, embedded systems can not dynamically generate components due to the strict memory restriction.
TINET+TECS statically generates components, and dynamically combines them.
Therefore,

In the proposed framework, software application can be developed by not only TECS method but also existing method.
Software appication can be developed as a TECS component because TINET+TECS is a component-based framework using TECS.
Moreover, TECS supports an adapter to call functions of TECS components from non TECS codes.
The legacy codes such as an existing application can be supported in the proposed framework.

This paper evaluates the overheads of execution time and memory consumption and the amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.

@@

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model and basic technologies, i.e., TINET and TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation and Demonstration} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

This section describes system model, including the basic technologies such as TINET and TECS.
System model of the proposed framework is shown as Fig. \ref{fig:SystemModel}.
TINET+TECS is a component-based TCP/IP protocol stack, so TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
CEP and REP (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings by TECS method.
Moreover, TECS adapter supports the legacy codes such as an existing application.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/SystemModel.pdf}
    \caption{System model}
    \label{fig:SystemModel}
\end{figure}

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{par:ASP3} \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.
Fig. \ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
% TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
Users transmit and receive the data using a Communication End Point (CEP) which is an interface like a socket.
In transmission process, headers are attached to the data body passed to the CEP at each protocol layer, and the data is transmitted from the network device.
In reception process, headers of the data body received in the network device are analyzed at each protocol layer, and the data is passed to the CEP.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{Hierarchy diagram of TINET and TOPPERS/ASP3}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/ComponentDiagram.pdf}
    \caption{Component Diagram}
    \label{fig:ComponentDiagram}
\end{figure}

@@

The components of protocol stack for TINET+TECS is shown as Fig. \ref{fig:ComponentProtocolStack}.
Note that some small particle components such as a kernel object, dataqueques, and semaphores are omitted to simplify the component diagram.
In TINET+TECS, the components are divided for each protocol, and the functionalities such as input function and output function are defined as each a component.
Therefore, software visibility is improving because of small grain components.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/ComponentProtocolStack.pdf}
    \caption{Component diagram of protocol stack}
    \label{fig:ComponentProtocolStack}
\end{figure}

@@

The original TINET eliminates dynamic memory control to meet the sever memory restriction of embedded systems.
A memory area for sending/receiving data in the protocol stack is allocated and released within an predetermined area.
Memory allocator component performs the elimination of dynamic memory control in TINET+TECS.
The component provides a requested memory area from the memory area statically allocated.

The memory allocator component connects to as many tFixedSizeMemoryPool as needed, shown as Fig. \ref{fig:tMemoryAllocator}.
tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 to alloc and release a memory area of the requested size. 
tFixedSizeMemoryPool components with various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
On the other hands, all components which need allocate and deallocate memory connect to the memory allocator component, e.g., tTCPInput and tEthernetOutput.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/tMemoryAllocator.pdf}
    \caption{Component diagram of tMemoryAllocator}
    \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

@@

{\it receive} is also a specifier for a caller receiving data from a callee such as {\it out}.
The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
While, in case of {\it out}, a callee writes data in the memory allocated by a caller, in case of {\it receive}, the callee allocates the data memory.
Deallocating the memory is performed in the caller in both cases.

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp,
    [in]int32_t size,
    [in]uint8_t align);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp,
    [out]int32_t *size,
    [in]uint8_t align);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{An example of send and receive}
\label{src:SendReceive}
\end{figure}

\subsubsection{Network timer component}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/DynamicConnection.pdf}
    \caption{Dynamic connection}
    \label{fig:DynamicConnection}
\end{figure}

TECS supports dynamic connection method as a novel functionality.
Dynamic connection is a method to switch the binding of components at runtime as shown in Fig. \ref{fig:DynamicConnection}.
Note that all components are statically generated in TECS.
TECS can optimize the overhead of componentization because components are statically configured.
Dynamically generating the components causes a lot of memory consumption, which is a serious propoblem for embedded systems with strict memory constraint.
The proposed framework realizes the componentization of TINET while satisfying the memory constraint, because components statically generate and dynamically connect in TECS.

TINET+TECS utilizes the dynamic connection to swith between CEP and REP components as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state waiting for connection request from clients\footnote{ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}\\tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout)}.
For example, when processing with HTTP protocol, CEP passively opens with REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \caption{Dynamic connection between CEP and REP}
    \label{fig:DynamicConnectionUseCase}
\end{figure}

To utilize dynamic connection, the selector should be defined.
The selector connects all the components that can be dynamically connnected, to refer the descripter of them.
Descriptor is an identifier to access the component.
cREP ports are call ports array, which connect the number of tREP cells (Line 9 in Fig. \ref{src:DynamicCDLcode}).
{\it [ref\_desc]} is described to identify the call port refers to descriptors. 
In the case of Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.

@@

TECS supports {\it Adapter} functionality which enables to call a function in TECS from existing C codes.
An adapter connects a TECS component, and links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.
Software developers can utilize an existing application for TECS owing to the adapter.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/TECS_Adapter.pdf}
    \caption{TECS Adapter}
    \label{fig:TECS_Adapter}
\end{figure}

@@

@@

{\bf uIP:}
uIP (microIP) is a very small TCP/IP stack intended for tiny 8-bit and 16-bit microcontrollers.
uIP only requires about five kilobytes of code size and several hundred bytes of RAM.
uIP has been ported to various systems and has found its way into many commercial products.
After ver. 1.0 is released, later versions of uIP, including uIPv6, are integrated with Contiki OS \cite{par:Contiki},\cite{url:Contiki}, an operating system to connect tiny microcontroller to the Internet.

{\bf lwIP:}
lwIP (lightweightIP) is a small TCP/IP implementation for embedded systems.
The focus of lwIP is to reduce memory resource while still having a full scale TCP.
lwIP requires about 40 kilobytes of ROM and tens of kilobytes of RAM.
lwIP is larger than uIP, but provides better throughput.

{\bf CiAO/IP:}

@@

In the future, the proposed framework will cooperate with mruby on TECS \cite{par:mrubyonTECS}.
Note that mruby is a scripting language for embedded systems \cite{par:mruby}.
We will support the functionality that TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.

>>>>

\setcounter{topnumber}{5}       % ページ上部の図表は 5 個まで
\def\topfraction{1.00}          % ページの上 1.00 まで図表で占めて可
\setcounter{bottomnumber}{5}    % ページ下部の図表は 5 個まで
\def\bottomfraction{1.00}       % ページの下 1.00 まで図表で占めて可
\setcounter{totalnumber}{10}    % ページあたりの図表は 10 個まで
\def\textfraction{0.04}         % ページうち本文が占める割合の下限

@@

This paper proposes a component-based TCP/IP protocol stack for embedded systems, i.e., TINET+TECS, to improve the configurability and scalability of TCP/IP software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} \cite{par:hr-tecs} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, which statically defines component behaviors and interconnections.
Thus, TECS can optimize the overhead of componentization.

In addition, satisfying the original TINET specification, the proposed framework utilizes dynamic connection, a method of TECS, to dynamically switch component bindings.
A general TCP/IP protocol server dynamically processes the requested port, i.e., HTTP (port: 80) and HTTPS (port: 443).
However, embedded systems are restricted dynamic processing due to the strict memory restriction.
TINET supports static generation of CEPs and REPs which are like sockets.
As TINET+TECS statically generates components and dynamically combines them as well as TINET, TINET+TECS reduces dynamically increasing memory consumption.

In the proposed framework, software applications can be developed by not only TECS method but also existing method.
The software applications can be developed as a TECS component because TINET+TECS is a component-based framework using TECS.
Moreover, TECS supports an adapter to call functions of TECS components from non TECS codes.
The adapter allows the use of existing TCP/IP applications without modification.

This paper evaluates the overheads of execution time and memory consumption and the amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.
Moreover, the advantages of dynamic connection in terms of memory consumption and the low overhead of the TECS adapter are demonstrated.

@@

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model and basic technologies, i.e., TINET and TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework and demonstrates the advantages.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

This section describes the system model of TINET+TECS, including the basic technologies such as TINET and TECS.
System model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
TINET+TECS is a component-based TCP/IP protocol stack, and the TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
CEPs and REPs (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings by TECS method.
Moreover, TECS adapter supports the legacy codes for existing TCP/IP applications.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/SystemModel.pdf}
    \caption{System model of TINET+TECS}
    \label{fig:SystemModel}
\end{figure}

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{par:ASP3} \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.

Fig. \ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
% TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
Users transmit and receive the data using a Communication End Point (CEP) which is an interface like a socket.
In transmission process, headers are attached to the data body passed to the CEP at each protocol layer, and the data is transmitted from the network device.
In reception process, headers of the data body received in the network device are analyzed at each protocol layer, and the data is passed to the CEP.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{Hierarchy diagram of TINET and TOPPERS/ASP3}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentDiagram.pdf}
    \caption{Component Diagram}
    \label{fig:ComponentDiagram}
\end{figure}

@@

The components of a protocol stack for TINET+TECS is shown in Fig. \ref{fig:ComponentProtocolStack}.
Note that some small particle components such as a kernel object, dataqueques, and semaphores are omitted to simplify the component diagram.
In TINET+TECS, the components are divided for each protocol, and the functionalities such as input function and output function are defined as each a component.
Therefore, software visibility is improving because of small grain components.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
    \caption{Component diagram of protocol stack}
    \label{fig:ComponentProtocolStack}
\end{figure}

@@

The original TINET eliminates dynamic memory control to meet the severe memory restriction of embedded systems.
A memory area for sending/receiving data in the protocol stack is allocated and released within a predetermined area.
Memory allocator component performs the elimination of dynamic memory control in TINET+TECS.
The component provides a requested memory area from the memory area statically allocated.

The memory allocator component connects to as many tFixedSizeMemoryPool as needed, shown in Fig. \ref{fig:tMemoryAllocator}.
tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 to alloc and release a memory area of the requested size. 
tFixedSizeMemoryPool components with various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
On the other hands, all components which need allocate and deallocate memory connect to the memory allocator component, e.g., tTCPInput and tEthernetOutput.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/tMemoryAllocator.pdf}
    \caption{Component diagram of tMemoryAllocator}
    \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

@@

{\it receive} is also a specifier for a caller receiving data from a callee such as {\it out}.
The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown in Fig. \ref{fig:SendReceive}.
While, in case of {\it out}, a callee writes data in the memory allocated by a caller, in case of {\it receive}, the callee allocates the data memory.
Deallocating the memory is performed in the caller in both cases.

As shown in Fig. \ref{src:SendReceive}, the arguments of sending and receiving data such as {\it outputp} and {\it inputp} are defines with the {\it send/receive} specifiers in the signature description.

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp,
    [in]int32_t size,
    [in]uint8_t align);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp,
    [out]int32_t *size,
    [in]uint8_t align);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description of the nic driver (An example of send/receive)}
\label{src:SendReceive}
\end{figure}

% \subsubsection{Network timer component}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnection.pdf}
    \caption{Dynamic connection}
    \label{fig:DynamicConnection}
\end{figure}

TECS supports dynamic connection as a new functionality.
Dynamic connection is a method to switch the binding of components at runtime as shown in Fig. \ref{fig:DynamicConnection}.
Note that all components are statically generated in TECS.
TECS can optimize the overhead of componentization because components are statically configured.
Dynamically generating the components causes a lot of memory consumption, which is a serious problem for embedded systems with strict memory constraint.
The proposed framework realizes the componentization of TINET while satisfying the memory constraint, because components statically generate and dynamically connect in TECS.

TINET+TECS utilizes the dynamic connection to switch between CEP and REP components as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state waiting for connection request from clients\footnote{ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}\\tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout)}.
For example, when processing with HTTP protocol, CEP passively opens with REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \caption{Dynamic connection between CEP and REP}
    \label{fig:DynamicConnectionUseCase}
\end{figure}

To utilize dynamic connection, the selector should be defined.
The selector connects all the components that can be dynamically connnected, to refer the descriptor of them.
Descriptor is an identifier to access the component \cite{par:optimization}.
cREP ports are call ports array, which connect the number of tREP cells (Line 9 in Fig. \ref{src:DynamicCDLcode}).
{\it [ref\_desc]} is described to identify the call port refers to descriptors. 
In the case of Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.

@@

TECS supports {\it Adapter} functionality which enables to call a function in TECS from existing C codes.
An adapter is implemented between C codes and a TECS component, and links a C function to a TECS function shown in Fig. \ref{fig:TECS_Adapter}.
In TINET+TECS, when the application calls an API such as {\it tcp\_snd\_dat}, the adapter component calls the function of tTCPCEP such as {\it eAPI\_sendData}.
Note that {\it tcp\_snd\_dat} is defined with the name {\it eAPI\_sendData} in TINET+TECS.
The adapter wraps the APIs used in the existing applications into TECS functions.
Therefore, software developers can utilize an existing TCP/IP application by using the adapter.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/TECS_Adapter.pdf}
    \caption{TECS adapter}
    \label{fig:TECS_Adapter}
\end{figure}

@@

\subsection{Performance of TINET+TECS}

To demonstrate the low overhead of TINET+TECS, we evaluated the execution time and the memory consumption of TINET+TECS compared with TINET.

The comparison of execution time between TINET and TINET+TECS is shown in Fig. \ref{fig:EvaluationOfExecutionTime}.
The APIs used for the evaluation are {\it tcp\_snd\_dat} to send TCP data and {\it tcp\_rcv\_dat} to receive TCP data.
For {\it tcp\_snd\_dat}, we measured the executing time from the API calling by the application to the return of the processing result.
In TINET+TECS, the process is performed in the order of tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed of Fig. \ref{fig:ComponentProtocolStack}.
For {\it tcp\_rcv\_dat}, we measured the execution time from the data receiving in the LAN driver to the data acquisition in the application.
In TINET+TECS, the process is performed in the order of tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication of Fig. \ref{fig:ComponentProtocolStack}.
The execution time of TINET+TECS is as well as that of TINET; the overhead is about 3 usec.
{\it send/receive} specifiers enable to access the buffer address without data copies.
Therefore, the overhead of componentization does not effect the execution time.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfExecutionTime.pdf}
    \caption{Execution time of TINET and TINET+TECS}
    \label{fig:EvaluationOfExecutionTime}
\end{figure}

The memory consumptions of TINET and TINET+TECS are compared in TABLE \ref{tab:EvaluationOfMemoryConsumption}.
The memory consumption of TINET+TECS increases about 2.5\% compared with TINET.
The processes and data to manage TECS components, such as initialization of cells, descriptors, function tables, and skeleton functions, cause the increase memory consumption.

\begin{table}[t]
    \centering
    \caption{Memory consumption of TINET and TINET+TECS}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                    &   text       &  data    &   bss      &  total     \\ \hline
        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
        \hline
        \multicolumn{5}{r}{Including the application and kernel objects}
    \end{tabular}
    \label{tab:EvaluationOfMemoryConsumption}
\end{table}

As shown in TABLE \ref{tab:EvaluationOfConfigurabilty}, the code lines for modification were measured to demonstrate the improved configurability.
We can change the composition of the protocol stack with a small workload.
Thus, the proposed framework improves the configurability.

\begin{table}[t]
    \centering
    \caption{Modified code lines of CDL}
    \begin{tabular}{c|r|r|r}
        \hline\hline
                         &   Size       &   Size (- Default)  & CDL  \\ \hline
        Default          &   325.23 KB  &             0 KB    &  0 lines   \\
        I                &   305.40 KB  &       - 19.83 KB    & 18 lines    \\
        I + I\hspace{-.1em}I &   304.12 KB  &   - 21.10 KB    & 27 lines   \\
        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & - 21.77 KB  & 32 lines \\
        \hline
        \multicolumn{4}{l}{I: Remove TCP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
    \end{tabular}
    \label{tab:EvaluationOfConfigurability}
\end{table}

\subsection{Dynamic Connection}

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
    \caption{Component diagrams of two cases (without/with dynamic connection)}
    \label{fig:ComparisonOfDynamicConnection}
\end{figure}

The memory consumption without and with TECS dynamic connection was evaluated.
As shown in the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP component should statically connect to all REP components in the case dynamic connection is not used.
As the number of REPs increases, call ports of CEP are required for that.
Thus, it consumes a lot of memory. 
Dynamic connection reduces the memory consumption because only one call port of CEP for REP, which is drawn with red lines in the right of Fig. \ref{fig:ComparisonOfDynamicConnection}, is required per CEP.
Even when the number of REPs increases, a call port of the selector, not the CEP, is joined.

The memory consumption of two cases, without/with dynamic connection, is shown in Fig. \ref{fig:EvaluationOfDynamicConnection}.
The case of dynamic connection consumes the RAM memory more than the other case because the call ports with {\it [dynamic]} is not optimized and allocated in RAM areas as mentioned in Section \ref{sec:DynamicConnection}.
The total memory consumption is fewer in the proposed framework.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
    \caption{Memory consumption of two cases (with/without dynamic connection)}
    \label{fig:EvaluationOfDynamicConnection}
\end{figure}

\begin{table}[t]
    \centering
    \caption{CDL code lines of without/with dynamic connection}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}

\begin{figure}[t]
 \centering
 \begin{lstlisting}
/* without Dynamic Connection */
cell tTCPCEP TCPCEP_000 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_001 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
..
cell tTCPCEP TCPCEP_00n {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
 \end{lstlisting}
 \centering
 \begin{lstlisting}
/* with Dynamic Connection */
cell tRepSelector RepSelector {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_000 {
    cRepSelector = RepSelector.eRepSelector;
};
cell tTCPCEP TCPCEP_001 {
    cRepSelector = RepSelector.eRepSelector;
};
..
cell tTCPCEP TCPCEP_00n {
    cRepSelector = RepSelector.eRepSelector;
};
 \end{lstlisting}
 \caption{Comparison of CDL descriptions between without/with dynamic connection}
 \label{src:ComparisonOfCDL}
\end{figure}

The comparison of CDL code lines of without/with dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection}, to demonstrate improved configurability by dynamic connection.
As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
In the left part of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
In the right part of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
Since the difference spreads as the number of CEPs and REPs increases, it is effective for software that uses many ports.

\subsection{Overhead of Adapter}

The execution time of API with the adapter such as {\it tcp\_snd\_dat/eAPI\_sendData} to analyze the overhead of TECS adapter which supports existing applications.
As shown in Fig. \ref{fig:EvaluationOfAdapter}, the overhead of TECS adapter is very small because the adapter only passes the parameters to TECS components from C codes.
Therefore, TECS adapter does not affect the system.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfAdapter.pdf}
    \caption{Execution time of two cases (without/with TECS adapter)}
    \label{fig:EvaluationOfAdapter}
\end{figure}

@@

{\bf uIP:}
uIP (microIP) is a very small TCP/IP stack intended for tiny 8-bit and 16-bit microcontrollers.
    uIP only requires about five KB of code size and several hundreds bytes of RAM.
uIP has been ported to various systems and has found its way into many commercial products.
After ver. 1.0 is released, later versions of uIP, including uIPv6, are integrated with Contiki OS \cite{par:Contiki},\cite{url:Contiki}, an operating system to connect tiny microcontroller to the Internet.

{\bf lwIP:}
lwIP (lightweightIP) is a small TCP/IP implementation for embedded systems.
The focus of lwIP is to reduce memory resource while still having a full scale TCP.
lwIP requires about 40 KB of ROM and tens of KB of RAM.
lwIP is larger than uIP, but provides better throughput.

% {\bf CiAO/IP:}
% \\
% \\
% Should be written
% \\
% \\

@@

This paper proposed TINET+TECS, a component-based TCP/IP protocol stack for embedded systems.
TINET+TECS is componentized TINET, which is a compact TCP/IP protocol stack, using TECS.
TINET consists of many macros and complicated codes and the software productivity are low.
The proposed framework improves the configurability while suppressing the overhead of componentization.
The proposed framework also improves the scalability because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.

In addition, this paper presents dynamic connection, a new method of TECS, to enable dynamic processing while reducing memory consumption.
To satisfy TINET specification that TINET support static generation of CEPs and REPs, TINET+TECS utilizes dynamic connection.
TECS adapter supports legacy codes, existing TCP/IP applications can run without modification in the proposed framework.

In the future, the proposed framework will cooperate with mruby on TECS \cite{par:mrubyonTECS} to easily manage IoT devices.
Note that mruby is a scripting language for embedded systems \cite{par:mruby}.
We will support the functionalities that TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.
